Online Balanced Graph Partitioning: Optimizations for Large Clusters

### 2020-05-03 paper/disc20clustering.tex
Rewrite

Across this paper, we often refer to groups of communicating nodes.
As this concept is used differently in the lower bound and the upper bounds, we name them differently to avoid confusion.

>>>>

Across this paper, we often refer to groups of communicating nodes.
We use this concept slightly differently in the lower bound and the upper bounds.
In our algorithms, we group communicating nodes into \emph{components}, and in the lower bound, we group nodes that may communicate into \emph{ground sets}.
